---
title: "Week2Day4interactive"
format: html
editor: visual
---

```{r}
library(tidyverse)
```

# Interactive Session 1

## Functions

```{r}
#verb then descriptor with arguments you want to expect
double_value <- function( my_dollars) {
  print(2 * my_dollars)
}

double_value(my_dollars = 10.13)
```

```{r}
double_value(10.13)
```

```{r}
#giving argument and R doesnt know what it is 
double_value(my_dollars = 10.13, 5)
```

```{r}
monthly_income <- c(42.50, 61.75, 89.50)

double_value(monthly_income)
```

```{r}
double_value2 <- function(dollars) {
  dollars * 2
}
#print is only show me this nothing stored, return statement is store this so i can use this later
double_value2(dollars =10) * 0.08
```

```{r}
#stores it
tax_double <- double_value2(dollars =10) * 0.08
```

### Create a function that returns an awesome restaurant name given a cool animal and your favorite food 

```{r}
#descriptive verb and non verb, animal and food are arguments, value into single string and printed 
name_restaraunt <- function(animal, food) {
  print(paste0(animal, food))
}
#if wanna use again create a function 
name_restaraunt(animal = "hawk", food = "pizza")

```

## given temperature in degrees Fahrenheit write a function that converts it to celsius 

```{r}

convert_celsius <- function(f_temp, c_temp) {
  print((f_temp - 32) * (5 / 9))
}
```

```{r}
convert_celsius(f_temp =52)
```

## Create a function given inputs age and home town returns I am this many years old and I'm from this home town

```{r}
return_agehome <- function(age, hometown) {
  print(paste("I am", age, "years old and I'm from", hometown,"."))
}

return_agehome(age = 6, hometown = "Los Angeles")
```

## Function with conditionals 

-   saves will now be in new branch made

```{r}
#age you calcualte will be absaed on animal 
calculate_animal_age <- function(species, age_human)
  if (species == "dog") {
    age_human * 7
  } else if (species == "goat") {
    age_human *4.7
    } else {
      print("Please enter dog or goat") #if none of other things happen do this 
  }

  
```

```{r}
calculate_animal_age(species = "dog", age_human * 10)

calcualte_animal_age(species = "goat", age_human = 4)

calculate_animal_age(species == "whale", age_human = 10)
#nothing happens, no errors, ifs statemenet arent evaluated because they dont go through condition to be evaluated 

```

## write a function that will return that given temperature in kelvin if a user selects "metric" to the scale then return degrees Celsius, or if they select "english" then return degrees in Fahrenheit 

```{r}
#use two arguments, input of temp in kelvin, two is user selection of metric or english based on selected return someething different

return_degrees <- function(scale, temp_k) {
  if(scale == "metric") {
    temp_k - 273.15
  } else if(scale == "english") {
    print(((temp_k - 273.15) * 1.8) + 32)
  }



```

```{r}
my_value = convert_kelvin(scale = "metric", temp_k = 40)
```
